---
title: "Variable Types and Special Values"
author: "Raha"
output: html_document
---

vectors have variables of _one_ type
```{r}
c(1, 2, "three")
(1:3) * 2
(1:4) * c(1, 2)
(1:4) * (1:3)
```
Each element of a vector can be given a name. This can be done by passing named arguments to
the c() function or later with the names function

```{r}
x <- c("red", "green", "blue")
capColor = c(huey = "red", duey = "blue", louie = "green")
```


```{r}
capColor["louie"]
names(capColor)[capColor == "blue"]
x <- c(4, 7, 6, 5, 2, 8)
I <- x < 6
J <- x > 7
x[I | J]
x[c(TRUE, FALSE)]
x[c(-1, -2)]

```
```{r}
x <- 1:10
x[c(TRUE, FALSE)] <- 1
x
```

A list is a generalization of a vector in that it can contain objects of different types, including
other lists. 
```{r}
L <- list(x = c(1:5), y = c("a", "b", "c"), z = capColor)
L
L[[2]]
L$y
L[c(1, 3)]
L[c("x", "y")]
L[["z"]]
```

A data.frame is not much more than a list of vectors, possibly of different types, but with
every vector (now columns) of the same length.
```{r}
d <- data.frame(x = 1:10, y = letters[1:10], z = LETTERS[1:10])

d[1]
d[, 1]
d[, "x", drop = FALSE]
d[c("x", "z")]
d[d$x > 3, "y", drop = FALSE]
d[2, ]
```

NA Stands for not available
```{r}
NA + 1
sum(c(NA, 1, 2))
median(c(NA, 1, 2, 3), na.rm = TRUE)
length(c(NA, 2, 3, 4))
3 == NA
NA == NA
TRUE | NA
```
NULL is special since it has no
class (its class is NULL) and has length 0 so it does not take up any space in a vector

```{r}
length(c(1, 2, NULL, 4))
sum(c(1, 2, NULL, 4))
x <- NULL
c(x, 2)

```
Inf Stands for infinity and only applies to vectors of class numeric. A vector of class integer can
never be Inf.
```{r}
pi/0
2 * Inf
Inf - 1e+10
Inf + Inf
3 < -Inf
Inf == Inf
```

NaN Stands for not a number. The result is unknown, but it is surely not a number.
```{r}
NaN + 1
Inf/Inf
exp(NaN)
class(NaN)
```


```{r}
```
